\addcontentsline{toc}{subsection}{References}
\begin{thebibliography}{99}

    \bibitem{Conway1963}
        {Conway, Melvin E.. "Design of a Separable Transition-Diagram Compiler".
         Commun. ACM, Volume 6 Issue 7, July 1963, Articale No. 7}

    \bibitem{Knuth1997}
        {Knuth, Donald Ervin (1997). "Fundamental Algorithms. The Art of Computer Programming 1", (3rd ed.).
         Addison-Wesley. Section 1.4.2: Coroutines}

    \bibitem{Moura2009}
        \href{http://www.inf.puc-rio.br/~roberto/docs/MCC15-04.pdf}
        {Moura, Ana L\'{u}cia De and Ierusalimschy, Roberto. "Revisiting coroutines".
         ACM Trans. Program. Lang. Syst., Volume 31 Issue 2, February 2009, Article No. 6}

    \bibitem{n3328}
        \href{http://www.open-std.org/jtc1/sc22/wg21/docs/papers/2012/n3328.pdf}
        {N3328: Resumable Functions}

    \bibitem{n3964}
        \href{http://www.open-std.org/jtc1/sc22/wg21/docs/papers/2014/n3964.pdf}
        {N3964: Library Foundations for Asynchronous Operations, Revision 1}.

    \bibitem{asio154}
        \href{http://www.boost.org/doc/libs/1_54_0/doc/html/boost_asio.html}
        {boost.asio}

    \bibitem{coroutine154}
        \href{http://www.boost.org}
        {boost.coroutine (proposed interface will be available in boost-1.55)}

    \bibitem{context154}
        \href{http://www.boost.org}
        {boost.context}

    \bibitem{abi}
        \href{http://en.wikipedia.org/wiki/Application_binary_interface}
        {Wikipedia - 'Application binary interface'}

    \bibitem{callingconvention}
        \href{http://en.wikipedia.org/wiki/Calling_convention}
        {Wikipedia - 'Calling convention'}

    \bibitem{awaite}
        \href{http://github.com/panaseleus/await_emu}
        {await\_emu by Evgeny Panasyuk}

    \bibitem{coroutineSum2006}
        \href{http://www.crystalclearsoftware.com/soc/coroutine/}
        {boost.coroutine by Giovanni P. Deretta, 'Google Summer of Code 2006'}

    \bibitem{mordor}
        \href{http://code.mozy.com/projects/mordor}
        {Mordor high performance I/O library}

    \bibitem{atnt1989}
        \href{http://www.softwarepreservation.org/projects/c_plus_plus/cfront/release_2.0/doc/LibraryManual.pdf}
        {AT\&T Task Library}

    \bibitem{gccsplit}
        \href{http://gcc.gnu.org/wiki/SplitStacks}
        {Split Stacks in GCC}

    \bibitem{channelnine}
        \href{http://channel9.msdn.com/Events/Build/2013/2-306#c635084523858527973}
        {channel9 - 'The Future of C++'}

    \bibitem{wikipedia}
        \href{http://en.wikipedia.org/wiki/Coroutine#Programming_languages_with_native_support}
        {Wikipedia - 'Coroutine'}

    \bibitem{yieldc}
        \href{http://www.boost.org/doc/libs/1_54_0/doc/html/boost_asio/reference/yield_context.html}
        {boost::asio::yield\_context}

\end{thebibliography}

